
\chapter{\label{cha:Preface}Preface}
It has been a thrilling journey since I started working on this thesis project. Although graph databases and regular path queries have already been studied since more than 20 years ago, combining them with latest technologies such as Apache Spark and Cassandra/HBase is still such a fresh and innovative experience for me. Besides, by following the development of the latest tools such as Titan, I came to understand why and how those projects can change the play in the big data world and real world.

First of all, I'd like to express gratitude for my supervisor dr.ir. Jan Hidders, who can always give the most helpful suggestions in a timely manner to keep the project forward, despite the fact that my 'stupid' ideas or grammar errors are coming up sometimes. At the same time, thanks to professor dr.ir. Geert Jan Houben and dr.ir. Ana Lucia Varbanescu for spending their precious time on reading my thesis and giving valuable feedback.

I want to give special thanks to Mr. Jeroen Schot from Surf Sara, who kept fighting against the bugs of Spark on Hbase and
 made my application run successfully on their cluster. Without his effort, Chapter 7 and 8 would only have some simple results from the expensive Google Cloud platform.
 
I am especially grateful to my parents and my girlfriend, who gave me both financial and spiritual support in the past years and finally helped me getting closer and closer to the master degree.

The guys in Alpha group, you are awesome and I can't be more lucky to work around you during the thesis project. Hope you are well and good luck with your future research.

\vskip1cm 

\begin{flushright}
\theauthor\\
 Delft, the Netherlands \\
 \today\\
 
\par\end{flushright}
